### 2020-08-10 data/draft-publications.tex
hyperlinks with title

\item S Aiyappan, A. K. Nandakumaran and Abu Sufian, \emph{Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure},  Mathematical Methods in the Applied Sciences {\bf 42} (2019. DOI: 10.1002/mma.5748), 6407-6434 , DOI 10.1002/mma.5748.
\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma, \emph{Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements}, Biomedical Optics Express 5395 {\bf 10} (2019), .
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash, \emph{Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains}, Annali di Matematica Pura ed Applicata {\bf 198} (2019), 1931-1954, DOI 10.1007/s10231-019-00848-7.
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash, \emph{Semi-linear optimal control problem on a smooth oscillating domain}, Communications in Contemporary Mathematics {\bf } (2019), 1-26, DOI 10.1142/S0219199719500299.
\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran, \emph{ Control Problem on a Rough Circular Domain and Homogenization}, Asymptotic Analysis {\bf 115} (2019),  19-46, DOI 10.3233/ASY-191526.
\item Khare, Apoorva and Rajaratnam, Bala, \emph{Probability inequalities and tail estimates for metric semigroups}, Advances in Operator Theory (Special issue in honor of Rajendra Bhatia) {\bf 5} (2020), 779-795, DOI 10.1007/s43036-020-00048-8, \url{https://link.springer.com/article/10.1007%2Fs43036-020-00048-8}.
\item Ghosh, Subhajit, \emph{Total Variation Cutoff for the Transpose Top-2 with Random Shuffle}, to appear in Journal of Theoretical Probability, DOI 10.1007/s10959-019-00945-6, \url{https://link.springer.com/article/10.1007%2Fs10959-019-00945-6}.
\item Datta, B. and Gupta, S., \emph{Semi-regular tilings of the hyperbolic plane \label{bdsg_2019} }, to appear in Discrete Comput Geom, DOI https://doi.org/10.1007/s00454-019-00156-0, \url{https://doi.org/10.1007/s00454-019-00156-0}.
\item Datta, B. and Sarkar, S., \emph{Equilibrium triangulations of some quasitoric 4-manifolds}, Southeast Asian Bull. Math. {\bf 44} (2020), 57--78.
\item Datta, B. and Maity, D., \emph{Correction to: Semi-equivelar and vertex-transitive maps on the torus}, Beitr Algebra Geom {\bf 61} (2020), 187--188.
\item Martin Kreuzer and Dilip P. Patil , \emph{COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS}, to appear in Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry.
\item Bharali, Gautam and Maitra, Anwoy, \emph{A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems}, to appear in Annali della Scuola Normale Superiore di Pisa, DOI 10.2422/2036-2145.201906_007, \url{http://annaliscienze.sns.it/index.php?page=ForthcomingArticles}.
\item Maitra, Anwoy, \emph{On the continuous extension of Kobayashi isometries}, Proc. Amer. Math. Soc. {\bf 148} (2020), 3437--3451, \url{https://www.ams.org/journals/proc/2020-148-08/S0002-9939-2020-15038-1/}.
\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, G. and Lakshmanan, M, \emph{On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation}, Physics Letters A {\bf 383} (2019), 15-26.
\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and Amritkar, R. E. and Rangarajan, G. and Ravindranath, V. and Ambika, G, \emph{Synapse loss and progress of Alzheimer’s disease - A network model}, Scientific Reports {\bf 9} (2019), 6555.
\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, G., \emph{On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation}, Chaos {\bf 29} (2019), 123135.
\item Sarkar, Amar Deep and Verma, Kaushal, \emph{A submultiplicative property of the Carath\'{e}odory metric on planar domains}, Proc. Indian Acad. Sci. (Math. Sci.) {\bf } (), , \url{https://www.ias.ac.in/article/fulltext/pmsc/130/0035}.
\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor, \emph{Higher Chern Classes in Iwasawa Theory}, American Journal of Mathematics {\bf 142} (2020), 627-682, \url{https://muse.jhu.edu/issue/42062}.
\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M., \emph{Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation}, to appear in Israel Journal of Mathematics.
\item M. K. Ghosh and S. Pradhan, \emph{Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant}, to appear in ESIAM: Control, Optimization and Calculus of Variations , DOI Doi:10.105/cocv/2020029.
\item M. K. Ghosh, K. Suresh Kumar, C. Pal and S. Pradhan, \emph{Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications}, to appear in Stochastic Analysis and Applications, DOI Doi: 10.1080/07362994.2020.1796707.
\item Iyer, S. K. and Yogeshwaran, D., \emph{Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes}, Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques {\bf 56} (2020), 1869-1897, \url{https://doi.org/10.1214/19-AIHP1020}.
\item Datta, Basudeb and Gupta, Subhojoy, \emph{Semi-regular tilings of the hyperbolic plane}, to appear in Discrete and Computational Geometry, DOI https://doi.org/10.1007/s00454-019-00156-0.
\item Thirupathi Gudi, Ramesh Ch. Sau, \emph{Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem}, to appear in ESAIM: Control, Optim. Calc. Var, DOI doi: 10.1051/cocv/2019068..
\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh, \emph{On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel},  Studia Math. {\bf 255} (2020), 83–107., DOI 10.4064/sm190505-8-10.
\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada, \emph{Toeplitz operators on the symmetrized bidisc}, International Mathematics Research Notices (IMRN) {\bf } (), , DOI 10.1093/imrn/rnz333.
\item Pingali, Vamsi Pritham and Varolin, Dror, \emph{Nonuniformly flat affine algebraic hypersurfaces}, to appear in Nagoya Mathematical Journal, DOI https://doi.org/10.1017/nmj.2019.2, \url{https://www.cambridge.org/core/journals/nagoya-mathematical-journal/article/nonuniformly-flat-affine-algebraic-hypersurfaces/3704C1133CB22A05D7FB13765156FC4E}.
\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham , \emph{Gravitating vortices and the Einstein–Bogomol’nyi equations}, to appear in Mathematische Annalen, DOI https://doi.org/10.1007/s00208-020-01964-z, \url{https://link.springer.com/content/pdf/10.1007/s00208-020-01964-z.pdf}.
\item Datar, Ved and Jacob,Adam and Zhang, Yuguang, \emph{Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces}, to appear in Journal of differential geometry, \url{https://arxiv.org/pdf/1809.08583.pdf}.
\item Datar, Ved and Pingali, Vamsi Pritham, \emph{On coupled constant scalar curvature Kaehler metrics}, to appear in Journal of symplectic geometry, \url{https://arxiv.org/pdf/1901.10454v2.pdf}.
\item Pradhan, P. and Sahu, B., \emph{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, Discrete Mathematics {\bf 343} (2020), , DOI 10.1016/j.disc.2020.112044, \url{https://doi.org/10.1016/j.disc.2020.112044}.
\item Arun Maiti, \emph{Quasi-vertex-transitive maps on the plane}, Discrete Mathematics {\bf 343} (2020), 111911-111917, \url{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}.
\item Datt, Gopal and Kumar, Sanjay, \emph{A criterion for quasinormality in $\mathbb{C}^n$},  Proc. Indian Acad. Sci. Math. Sci. {\bf 129} (2019), Paper No. 11, 13 pp., DOI https://doi.org/10.1007/s12044-018-0449-5     (This article was published before the review period i.e., April 1, 2019, BUT this is not yet included on the page  https://siddhartha-gadgil.github.io/DeptWeb/pubs.html), \url{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}.
\item Hatui, Sumana, \emph{Schur multipliers of special p-groups of rank 2}, Journal of Group Theory {\bf 23} (2020), 85-95, DOI https://doi.org/10.1515/jgth-2019-0045, \url{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}.
\item Choudhury, Projesh Nath and Tsatsomeros Michael J., \emph{Algorithmic Detection and Construction of N-matrices}, Linear Algebra and Its Applications {\bf 602} (2020), 46-56, DOI 10.1016/j.laa.2020.04.028, \url{https://doi.org/10.1016/j.laa.2020.04.028}.
\item Choudhury, Projesh Nath and Sivakumar, K.C., \emph{Matrices with Positive Semidefinite Real Part}, to appear in Linear and Multilinear Algebra, DOI 10.1080/03081087.2019.1602588, \url{https://doi.org/10.1080/03081087.2019.1602588}.
\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala , \emph{On Baker's explicit abc-conjecture},  Publ. Math. Debrecen {\bf 94} (2019), 435–453.
\item Carstensen, C. and Mallik, G. and Nataraj, N., \emph{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, IMA Journal of Numerical Analysis {\bf } (2020), , DOI https://doi.org/10.1093/imanum/drz071, \url{https://doi.org/10.1093/imanum/drz071}.
\item Mal, Arpita and Sain, Debmalya and Paul, Kallol, \emph{On some geometric properties of operator spaces}, Banach J. Math. Anal. {\bf 13} (2019), 174-191, \url{https://projecteuclid.org/euclid.bjma/1543914019}.

@@

Samu, {\em The exact phase diagram for a semipermeable {TASEP} with
nonlocal boundary jumps}, J. Phys. A} {\bf 52} (2019), 355001, 19, DOI 10.1088/1751-8121/ab2e96, \url{https://doi.org/10.1088/1751-8121/ab2e96}.

@@

Nandakumaran, A. K., {\em Control problem on a rough circular domain and homogenization}, Asymptot. Anal.} {\bf 115} (2019), 19--46, DOI 10.3233/asy-191526, \url{https://doi.org/10.3233/asy-191526}.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Locally periodic unfolding operator for highly oscillating
rough domains}, Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954, DOI 10.1007/s10231-019-00848-7, \url{https://doi.org/10.1007/s10231-019-00848-7}.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi, {\em Generalization of unfolding operator for highly oscillating
smooth boundary domains and homogenization}, Calc. Var. Partial Differential Equations} {\bf 57} (2018), Art. 86, 30, DOI 10.1007/s00526-018-1354-6, \url{https://doi.org/10.1007/s00526-018-1354-6}.
\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu, {\em Asymptotic analysis of a boundary optimal control problem on a
general branched structure}, Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434, DOI 10.1002/mma.5748, \url{https://doi.org/10.1002/mma.5748}.
\item Aiyappan, S. and Sardar, Bidhan Chandra, {\em Biharmonic equation in a highly oscillating domain and

>>>>

\item S Aiyappan, A. K. Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019. DOI: 10.1002/mma.5748), 6407-6434.
\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954.
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26.
\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
\item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
\item Martin Kreuzer and Dilip P. Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, G. and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and Amritkar, R. E. and Rangarajan, G. and Ravindranath, V. and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf } ().
\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
\item M. K. Ghosh and S. Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
\item M. K. Ghosh, K. Suresh Kumar, C. Pal and S. Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
\item Iyer, S. K. and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
\item Thirupathi Gudi, Ramesh Ch. Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim. Calc. Var}.
\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
\item Pradhan, P. and Sahu, B.: A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd, \emph{Discrete Mathematics} {\bf 343} (2020).
\item Arun Maiti: Quasi-vertex-transitive maps on the plane, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
\item Datt, Gopal and Kumar, Sanjay: A criterion for quasinormality in $\mathbb{C}^n$, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Paper No. 11, 13 pp..
\item Hatui, Sumana: Schur multipliers of special p-groups of rank 2, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: Algorithmic Detection and Construction of N-matrices, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
\item Choudhury, Projesh Nath and Sivakumar, K.C.: Matrices with Positive Semidefinite Real Part, to appear in \emph{Linear and Multilinear Algebra}.
\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
\item Carstensen, C. and Mallik, G. and Nataraj, N.: Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: On some geometric properties of operator spaces, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174-191.
\item Roth, Julien and Upadhyay, Abhitosh: On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
\item Roth, Julien and Upadhyay, Abhitosh: f-Biharmonic Submanifolds of Generalized Space Forms, \emph{Results in Mathematics} {\bf 75} (2020).
\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.

\subsection{Papers in Journals with links}
\item S Aiyappan, A. K. Nandakumaran and Abu Sufian: Asymptotic analysis of Boundary Optimal Control Problem on a General Branched Structure, \emph{Mathematical Methods in the Applied Sciences} {\bf 42} (2019. DOI: 10.1002/mma.5748), 6407-6434.
\item K. Murali, A. K. Nandakumaran, Turgurt Durduran, Hari M Varma: Recovery of the diffuse correlation spectroscopy data-type from speckle contrast measurements: towards low-cost, deep-tissue blood flow measurements, \emph{Biomedical Optics Express 5395} {\bf 10} (2019).
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Locally Periodic Unfolding Operator for Highly Oscillating Rough Domains, \emph{Annali di Matematica Pura ed Applicata} {\bf 198} (2019), 1931-1954.
\item S Aiyappan, A. K. Nandakumaran and Ravi Prakash: Semi-linear optimal control problem on a smooth oscillating domain, \emph{Communications in Contemporary Mathematics} {\bf } (2019), 1-26.
\item S Aiyappan, Editha C. Jose, Ivy Carol B. Lomerio and A. K. Nandakumaran: Control Problem on a Rough Circular Domain and Homogenization, \emph{Asymptotic Analysis} {\bf 115} (2019), 19-46.
\item M. Balodi, A. Banerjee, S. Ray: Cohomology of modules over H-categories and co-H-categories, to appear in \emph{Canadian Journal of Mathematics}.
\item M. Balodi, A. Banerjee, S. Ray: Entwined modules over linear categories and Galois extensions, to appear in \emph{Israel Journal of Mathematics (Accepted)}.
\item A. Banerjee: On Noetherian schemes over $(\mathcal C,\otimes,1)$ and the category of quasi-coherent sheaves, to appear in \emph{Indiana University Mathematics Journal}.
\item A. Banerjee: On differential torsion theories and rings with several objects, \emph{Canadian Math Bulletin} {\bf 62} (2019), 703--714.
\item Khare, Apoorva and Rajaratnam, Bala: Probability inequalities and tail estimates for metric semigroups, \emph{Advances in Operator Theory (Special issue in honor of Rajendra Bhatia)} {\bf 5} (2020), 779-795.
\item Ghosh, Subhajit: Total Variation Cutoff for the Transpose Top-2 with Random Shuffle, to appear in \emph{Journal of Theoretical Probability}.
\item Datta, B. and Gupta, S.: Semi-regular tilings of the hyperbolic plane \label{bdsg_2019}, to appear in \emph{Discrete Comput Geom}.
\item Datta, B. and Sarkar, S.: Equilibrium triangulations of some quasitoric 4-manifolds, \emph{Southeast Asian Bull. Math.} {\bf 44} (2020), 57--78.
\item Datta, B. and Maity, D.: Correction to: Semi-equivelar and vertex-transitive maps on the torus, \emph{Beitr Algebra Geom} {\bf 61} (2020), 187--188.
\item Martin Kreuzer and Dilip P. Patil: COMPUTATIONAL ASPECTS OF BURNSIDE RINGS PART II: IMPORTANT MAPS, to appear in \emph{Beiträge zur Algebra und Geometrie / Contributions to Algebra and Geometry}.
\item Gadadhar Misra: Professor, \emph{Adv. Math.} {\bf 351} (2019), 1105 - 1138.
\item Bharali, Gautam and Maitra, Anwoy: A weak notion of visibility, a family of examples, and Wolff--Denjoy theorems, to appear in \emph{Annali della Scuola Normale Superiore di Pisa}.
\item Maitra, Anwoy: On the continuous extension of Kobayashi isometries, \emph{Proc. Amer. Math. Soc.} {\bf 148} (2020), 3437--3451.
\item Vishnu Priya, N. and Senthilvelan, M. and  Rangarajan, G. and Lakshmanan, M: On symmetry preserving and symmetry broken bright, dark and antidark soliton solutions of nonlocal nonlinear Schrödinger equation, \emph{Physics Letters A} {\bf 383} (2019), 15-26.
\item Kashyap, G. A. R. S. R. K. and Bapat, D. and Das, D. and Gowaikar, R. D. and Amritkar, R. E. and Rangarajan, G. and Ravindranath, V. and Ambika, G: Synapse loss and progress of Alzheimer’s disease - A network model, \emph{Scientific Reports} {\bf 9} (2019), 6555.
\item Vishnu Priya, N. and Senthilvelan, M. and Rangarajan, G.: On the role of four-wave mixing effect in the interactions between nonlinear modes of coupled generalized nonlinear Schrodinger equation, \emph{Chaos} {\bf 29} (2019), 123135.
\item Sarkar, Amar Deep and Verma, Kaushal: A submultiplicative property of the Carath\'{e}odory metric on planar domains, \emph{Proc. Indian Acad. Sci. (Math. Sci.)} {\bf } ().
\item Frauke Bleher, Ted Chinburg, Ralph Greenberg, Mahesh Kakde, George Pappas, Romyar Sharifi, Martin Taylor: Higher Chern Classes in Iwasawa Theory, \emph{American Journal of Mathematics} {\bf 142} (2020), 627-682.
\item Basu, R. and Ganguly, S. and Hegde, M. and Krishnapur, M.: Lower Deviations in β-ensembles and Law of Iterated Logarithm in Last Passage Percolation, to appear in \emph{Israel Journal of Mathematics}.
\item M. K. Ghosh and S. Pradhan: Zero-Sum Risk-Sensitive Stochastic Differential Games with Reflecting Diffusions in the Orthant, to appear in \emph{ESIAM: Control, Optimization and Calculus of Variations}.
\item M. K. Ghosh, K. Suresh Kumar, C. Pal and S. Pradhan: Nonzero-sum risk-sensitive stochastic differential games with discounted costs, Stochastic Analysis and Applications, to appear in \emph{Stochastic Analysis and Applications}.
\item Iyer, S. K. and Yogeshwaran, D.: Thresholds for vanishing of isolated faces in random Cech and Vietoris-Rips Complexes, \emph{Annals de l'Institut Henri Poincar$\acute{e}$ - Probabiliti$\acute{e}$s et Statistiques} {\bf 56} (2020), 1869-1897.
\item Datta, Basudeb and Gupta, Subhojoy: Semi-regular tilings of the hyperbolic plane, to appear in \emph{Discrete and Computational Geometry}.
\item Thirupathi Gudi, Ramesh Ch. Sau: Finite Element Analysis of the Constrained Dirichlet Boundary Control Problem Governed by the Diffusion Problem, to appear in \emph{ESAIM: Control, Optim. Calc. Var}.
\item Bhattacharyya, Tirthankar and Biswas, Anindya and Chandel, Vikramjeet Singh: On the Nevanlinna problem: characterization of all Schur–Agler class solutions affiliated with a given kernel, \emph{Studia Math.} {\bf 255} (2020), 83–107..
\item Bhattacharyya, Tirthankar and Das, Bata Krishna and Sau, Haripada: Toeplitz operators on the symmetrized bidisc, \emph{International Mathematics Research Notices (IMRN)} {\bf } ().
\item Pingali, Vamsi Pritham and Varolin, Dror: Nonuniformly flat affine algebraic hypersurfaces, to appear in \emph{Nagoya Mathematical Journal}.
\item Alvarez-Consul, Luis and Garcia-Fernandez, Mario  and García-Prada, Oscar and Pingali, Vamsi Pritham: Gravitating vortices and the Einstein–Bogomol’nyi equations, to appear in \emph{Mathematische Annalen}.
\item Datar, Ved and Jacob,Adam and Zhang, Yuguang: Adiabatic limits of anti-self-dual connections on collapsed K3 surfaces, to appear in \emph{Journal of differential geometry}.
\item Datar, Ved and Pingali, Vamsi Pritham: On coupled constant scalar curvature Kaehler metrics, to appear in \emph{Journal of symplectic geometry}.
\item Pradhan, P. and Sahu, B.: \href{https://doi.org/10.1016/j.disc.2020.112044}{A characterization of the family of secant lines to a hyperbolic quadric in PG(3,q), q odd}, \emph{Discrete Mathematics} {\bf 343} (2020).
\item Arun Maiti: \href{https://www.sciencedirect.com/science/article/pii/S0012365X20301035}{Quasi-vertex-transitive maps on the plane}, \emph{Discrete Mathematics} {\bf 343} (2020), 111911-111917.
\item Datt, Gopal and Kumar, Sanjay: \href{https://link.springer.com/article/10.1007/s12044-018-0449-5?shared-article-renderer}{A criterion for quasinormality in $\mathbb{C}^n$}, \emph{Proc. Indian Acad. Sci. Math. Sci.} {\bf 129} (2019), Paper No. 11, 13 pp..
\item Hatui, Sumana: \href{https://www.degruyter.com/view/journals/jgth/23/1/article-p85.xml}{Schur multipliers of special p-groups of rank 2}, \emph{Journal of Group Theory} {\bf 23} (2020), 85-95.
\item Choudhury, Projesh Nath and Tsatsomeros Michael J.: \href{https://doi.org/10.1016/j.laa.2020.04.028}{Algorithmic Detection and Construction of N-matrices}, \emph{Linear Algebra and Its Applications} {\bf 602} (2020), 46-56.
\item Choudhury, Projesh Nath and Sivakumar, K.C.: \href{https://doi.org/10.1080/03081087.2019.1602588}{Matrices with Positive Semidefinite Real Part}, to appear in \emph{Linear and Multilinear Algebra}.
\item Chim, Kwok Chi; Shorey, Tarlok Nath; Sinha, Sneh Bala: On Baker's explicit abc-conjecture, \emph{Publ. Math. Debrecen} {\bf 94} (2019), 435–453.
\item Carstensen, C. and Mallik, G. and Nataraj, N.: \href{https://doi.org/10.1093/imanum/drz071}{Nonconforming Finite Element Discretization for Semilinear Problems with Trilinear Nonlinearity}, \emph{IMA Journal of Numerical Analysis} {\bf } (2020).
\item Mal, Arpita and Sain, Debmalya and Paul, Kallol: \href{https://projecteuclid.org/euclid.bjma/1543914019}{On some geometric properties of operator spaces}, \emph{Banach J. Math. Anal.} {\bf 13} (2019), 174-191.
\item Roth, Julien and Upadhyay, Abhitosh: \href{https://www.cambridge.org/core/journals/bulletin-of-the-australian-mathematical-society/article/on-almost-stable-cmc-hypersurfaces-in-manifolds-of-bounded-sectional-curvature/E0BF84D4D46C82F6D75CDCEAAF5DEE94}{On almost stable CMC hypersurfaces in manifolds of bounded sectional curvature}, \emph{Bulletin of the Australian Mathematical Society} {\bf 101} (2020), 333-338.
\item Roth, Julien and Upadhyay, Abhitosh: \href{https://link.springer.com/article/10.1007/s00025-019-1142-4?shared-article-renderer#citeas}{f-Biharmonic Submanifolds of Generalized Space Forms}, \emph{Results in Mathematics} {\bf 75} (2020).
\item Barbosa, Ezequiel and Santana, Farley and Upadhyay, Abhitosh: On stable CMC free-boundary surfaces in a strictly convex domain of a bi-invariant Lie group, to appear in \emph{International Journal of Mathematics}.

@@

Samu: The exact phase diagram for a semipermeable {TASEP} with
nonlocal boundary jumps, \emph{J. Phys. A} {\bf 52} (2019), 355001, 19.

@@

Nandakumaran, A. K.: Control problem on a rough circular domain and homogenization, \emph{Asymptot. Anal.} {\bf 115} (2019), 19--46.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Semi-linear optimal control problem on a smooth oscillating
domain, \emph{Commun. Contemp. Math.} {\bf 22} (2020), 1950029, 26.
\item Aiyappan, S. and Nandakumaran, A. K. and Prakash, Ravi: Locally periodic unfolding operator for highly oscillating
rough domains, \emph{Ann. Mat. Pura Appl. (4)} {\bf 198} (2019), 1931--1954.
\item Aiyappan, S. and Nandakumaran, A. K. and Sufian, Abu: Asymptotic analysis of a boundary optimal control problem on a
general branched structure, \emph{Math. Methods Appl. Sci.} {\bf 42} (2019), 6407--6434.
\item Aiyappan, S. and Sardar, Bidhan Chandra: Biharmonic equation in a highly oscillating domain and
homogenization of an associated control problem, \emph{Appl. Anal.} {\bf 98} (2019), 2783--2801.
\item Akutagawa, Kazuo and Endo, Hisaaki and Seshadri, Harish: A gap theorem for positive {E}instein metrics on the
four-sphere, \emph{Math. Ann.} {\bf 373} (2019), 1329--1339.
\item Anamby, Pramath and Das, Soumya: Distinguishing {H}ermitian cusp forms of degree 2 by a certain
